### 2022-06-18 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@506bc1d784de934764c8930b355a97ca76bf72b2 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@a96092b77ff5073ad066e801b83b0b46226f9a7f 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@a8599f92e7684e7f5aa8cbbacbf5433ffb071768 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@117ac6d708db764dee6f23f4aa7b357f4c88fc51 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@1ae0189d3cedf179e3b39cad8719776eccbbb86a 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b8ffddb

@@

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Predicting metawebs: transfer of graph
embeddings can help alleviate spatial data deficiencies}
\vskip 5em

>>>>

\DeclareDelayedFloatFlavour*{longtable}{table}

@@

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily The prediction of species interaction networks
is facilitated by graph embedding and transfer learning despite data
limitations}
\vskip 5em
